---
title: "Data Products - Week3 Presentation with Plotly"
author: "Pete Petersen"
date: "7/21/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Data Project

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

#### The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?  
2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?  


## Slide with R Output

```{r libraries, message=FALSE, echo=TRUE, warning=FALSE}

list.of.packages <- c("plotly","dplyr","data.table")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages,repos='http://cran.us.r-project.org')
library(dplyr)
library(plotly)

```

## Pressure vs. Temperature

```{r pressure, echo=FALSE, message=FALSE}
plot_ly(pressure, x =pressure$temperature, y = pressure$pressure)
```

